Self Regulation Ontology Retest Data Report

### 2017-03-20 SRO_Report.Rmd
working on new report

@@

  # transform variables
  # log transform for positive skew
  positive_subset = log(positive_subset)
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

@@

Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way.

**Question: Should I be removing outliers from the retest data? Or keep them if they were within the ranges in the test data even if they aren't in the retest data. Right now I'm removing them depending on t2 distributions**

Remove outliers from retest data the way they have been from test data
```{r}
clean_retest_data = cbind(sub_id = retest_data$sub_id, as.data.frame(apply(retest_data[, -which(names(retest_data) %in% c("sub_id"))], 2, remove_outliers)))
```

@@

```{r}
for(i in 1:length(names(clean_retest_data))){
  tmp_col = names(clean_retest_data)[i]
  if(tmp_col %in% logTr_vars$var){
    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
      if(sign == 'positive'){
        clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
        cat('\n')
      }
      else if(sign == 'negative'){
        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
        cat('\n')
      }
    }
}
```

>>>>

pos_log <- function(column){
  col_min = min(column, na.rm=T)
  a = 1-col_min
  column = column+a
  return(log(column))
}

@@

  # transform variables
  # log transform for positive skew
  # positive_subset = log(positive_subset)
  positive_subset = pos_log(positive_subset) #slight divergence from original code
  successful_transforms = as.data.frame(apply(positive_subset, 2, skew))
  names(successful_transforms) = c('skew')
  successful_transforms$dv = row.names(successful_transforms)
  successful_transforms = successful_transforms %>% filter(abs(skew)<threshold)
  successful_transforms = successful_transforms$dv
  successful_transforms = positive_subset[,successful_transforms]
  dropped_vars = names(positive_subset) %w/o% names(successful_transforms)

@@

Instead of applying the same functions applied to t1 data we check which variables are transformed in what way and transform the t2 data the same way. Again we are not removing outliers in the t2 or dropping variables if the skew is not removed successfully after transforming.

@@

```{r warning=FALSE}
clean_retest_data = retest_data

for(i in 1:length(names(clean_retest_data))){
  tmp_col = names(clean_retest_data)[i]
  if(tmp_col %in% logTr_vars$var){
    sign = logTr_vars$sign[which(tmp_col == logTr_vars$var)]
      if(sign == 'positive'){
        # clean_retest_data[,tmp_col] = log(clean_retest_data[,tmp_col])
        clean_retest_data[,tmp_col] = pos_log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.logTr')
        cat(paste0(tmp_col ,' was positively skewed and transformed.'))
        cat('\n')
      }
      else if(sign == 'negative'){
        clean_retest_data[,tmp_col] = neg_log(clean_retest_data[,tmp_col])
        names(clean_retest_data)[which(names(clean_retest_data) == tmp_col)] = paste0(tmp_col, '.ReflogTr')
        cat(paste0(tmp_col ,' was negatively skewed and transformed.'))
        cat('\n')
      }
    }
}
```
